\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{array}
\usepackage{caption}
\usepackage{float}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{pdflscape}
\usepackage{hyperref}
\usepackage[numbers]{natbib}

\hypersetup{
  colorlinks=true,
  linkcolor=black,
  citecolor=black,
  urlcolor=blue,
  pdftitle={The Sugar Paradox: National food supply predicts obesity across countries but not within them},
  pdfauthor={Blinded for review}
}

\setstretch{1.1}
\captionsetup{font=small}

\title{The Sugar Paradox: National food supply predicts obesity across countries but not within them}
\author{Blinded for review}
\date{}

\begin{document}
\maketitle

\begin{abstract}
Countries that eat more sugar are fatter.
Across 37 Sub-Saharan African countries, national sugar supply predicts women's obesity at $r = 0.50$ after controlling for income, urbanization, and vegetable oil supply.
The association survives every cross-sectional stress test: leave-one-out exclusion, subregion fixed effects, rank correlations.

Following the same countries over time resolves the association into between-country structure.
In a 2010--2022 panel, six within-country specifications---fixed effects, two-way fixed effects, detrending, first differences, long differences, and correlated random effects---all center the sugar coefficient near zero.
The boundary extends across food measures. Ten FAOSTAT food groups, plus grand-total energy, fat, and protein supply, lose predictive value under the same within-country tests. Entity and year fixed effects absorb 99.4\% of obesity variance, leaving 0.6\% for food-supply variables to explain.

A soybean oil case study exposes the failure mode. Soybean oil passes cross-sectional tests, one-way fixed effects, and Oster bounds ($\delta = 17.6$), yet its lead-lag ratio is 0.99---pure co-trending with no temporal direction. The same trend structure is global: 98\% of 200 countries show linear obesity trajectories ($R^2 \geq 0.90$).

The strongest predictor of which countries gained more obesity is how much obesity they had to start with ($t = 3.45$). Cross-sectional food-obesity associations---including those cited in support of sugar-sweetened beverage taxes---estimate shared development gradients. Causal dietary effects require designs with within-unit shocks, subnational panels, or individual longitudinal data.
\end{abstract}

\input{sections/introduction}
\input{sections/data}
\input{sections/paradox}
\input{sections/diagnosis}
\input{sections/global}
\input{sections/predictors}
\input{sections/discussion}

\section*{Data and Code Availability}
All data and code required to reproduce the analyses in this paper are publicly available at \url{https://github.com/mamboanye/sugar-paradox}.

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
