\section{Introduction}

Countries that consume more sugar are fatter. Plot national sugar supply against adult obesity prevalence for 37 Sub-Saharan African countries and the correlation is strong: $r = 0.50$ after controlling for GDP, urbanization, and vegetable oil supply ($p = 0.002$). Drop any single country and the result holds (leave-one-out range: 0.42--0.63). Add subregion fixed effects and the correlation strengthens to $r = 0.63$. By every conventional cross-sectional standard, sugar supply predicts obesity.

This paper shows that the association is entirely misleading. When we follow the same 37 countries over 13 years, tracking whether rising or falling sugar supply corresponds to faster or slower obesity growth, the association vanishes. Country fixed effects reduce the sugar coefficient to $t = 0.25$. Adding year effects drops it to $t = -0.64$. Detrending each country's individual trajectory gives $t = -0.13$. Three further approaches confirm the null: first differences ($r = -0.03$), long differences over the full decade ($r = -0.19$), and a Mundlak correlated random effects model ($t = -0.66$). Six specifications, each removing a different class of confounding, converge on the same answer: no signal.

The explanation is structural. Obesity has risen along near-linear trajectories in virtually every country over the past decade, and these trajectories have little to do with food supply. Entity and year fixed effects together absorb 99.4\% of obesity variance in our panel. Food supply variables compete for the remaining 0.6\%, a residual space dominated by measurement error and short-run noise. None of the 10 FAOSTAT food groups we test predicts within-country obesity. The null is not specific to sugar.

The mechanism is not subtle. Cross-sectional studies compare countries at a point in time, and such comparisons conflate persistent between-country differences with the shared upward trend in obesity. A correlated random effects decomposition confirms this: the between-country sugar coefficient is $t = 3.46$ while the within-country coefficient is $t = -0.66$. The entire association is between-country. A soybean oil case study makes the mechanism concrete. Soybean oil supply passes the same cross-sectional and one-way fixed-effects tests that sugar passes, yet its lead-lag ratio is 0.99: pure co-trending with no temporal direction.

The paradox matters because cross-sectional food supply studies have shaped policy. Basu et al.\ \cite{basu2013} applied generalized estimating equations to repeated cross-sections in 175 countries and argued that sugar availability independently predicted diabetes prevalence. A companion study \cite{basu2013ajph} linked soft drink consumption to overweight across 75 countries using purely cross-sectional regression, a finding cited over 500 times and invoked in WHO guidance on sugar-sweetened beverage taxation \cite{who2023ssb}. Both studies draw their identification from between-country variation, exactly the variation we show is confounded by shared trends. More broadly, the Global Burden of Disease project assigns diet-attributable deaths using food supply data that faces the same trend-domination problem \cite{gbd2019}, and a recent global analysis attributed 2.2 million new diabetes cases to sugar-sweetened beverages using dietary intake estimates informed in part by national food supply data \cite{laracastor2025}. Any study that relies on cross-national food supply variation to identify dietary effects inherits the confounding structure we document.

The problem is not specific to Sub-Saharan Africa. Among 200 countries in the NCD-RisC database \cite{ncdrisc2024bmi}, 98\% show linear obesity trends with $R^2 \geq 0.90$ over 2010--2021. This near-universal linearity means that any food supply variable trending over the same period will correlate with obesity cross-sectionally, regardless of whether it causes obesity.

If food supply changes do not predict obesity change, what does? The only predictor is initial obesity level ($t = 3.45$, $R^2 = 0.41$). Countries that started with higher obesity in 2010 gained more over the following decade. This divergence pattern points to structural economic and demographic conditions rather than dietary composition as the driver of cross-country obesity differences.

The paper proceeds as follows. Section 2 describes the data. Section 3 documents the paradox. Section 4 diagnoses why it exists. Section 5 shows the problem is global and revisits published results. Section 6 examines what does predict obesity change. Section 7 discusses implications.
